Addition and removal energies of circular quantum dots

### 2017-06-19 Manuscript/paper.tex
Made Morten and Nathan changes to CC sections

Using the coupled cluster wave function, the Schr\"odinger equation,
\begin{align} \label{eq:cc_schrodeq}
  \hat{H} \E^{\hat{T}} \ket{\Phi} = E \E^{\hat{T}} \ket{\Phi},
\end{align}
can be rewritten by left-multiplying by $\bra{\Phi}e^{-T}$ as,
\begin{align*}
  \bra{\Phi} \bar{H}_{\mathrm{CC}} \ket{\Phi} = E,
\end{align*}
where we define a coupled-cluster effective Hamiltonian,
\begin{align} \label{eq:cc_heff0}
  \bar{H}_{\mathrm{CC}} \equiv \E^{-\hat{T}} \hat{H} \E^{\hat{T}},
\end{align}
in which the wave operator, $\E^{\hat{T}}$, acts as a similarity transform on the Hamiltonian in the same way that $\hat{U}(s)$ acts to transform the Hamiltonian in SRG methods.  An important difference, however, is that the coupled cluster wave operator is not unitary, and thus $\bar{H}$ is not Hermitian.

@@

In practice, the cluster operator $\hat{T}$ must be truncated to be computationally feasible.  In this paper, we truncate it to only single and double excitations,
\begin{align*}
  \hat{T} = \hat{T}_1 + \hat{T}_2.
\end{align*}
This is known as coupled cluster singles and doubles (CCSD), with an asymptotic computational cost that scales like IM-SRG(2).  This truncation has been successfully applied to many problems in quantum chemistry \cite{RevModPhys.79.291} and nuclear physics \cite{0034-4885-77-9-096302}.  In addition, we also truncate the three-body effective Hamiltonian terms that are induced by the similarity transformation.  Figure \ref{fig:diagrams-ccsd} shows the diagrammatic representation of Eq.\ \eqref{eq:cc_heff1} in CCSD.

\begin{figure}
  \includegraphics{fig-diagrams-ccsd.pdf}
  \caption{(Color online) Diagrammatic representation of $\bar{H}$ of Eq.\ \eqref{eq:cc_heff1}, where open circles represent the excitation cluster operators $\hat{T}_1$ and $\hat{T}_2$, and filled circles represent the two-body interaction $\hat{H}_2$.  As before, the diagrams are implicitly antisymmetrized (Hugenholtz diagrams).  Lines connected to $\hat{T}$ are always directed upward because they represent an excitation operator while the directions of external lines connected to $\hat{H}_2$ are unconstrained.}
  \label{fig:diagrams-ccsd}
\end{figure}

>>>>

Using the coupled cluster wave function, the Schr\"odinger equation,
\begin{align} \label{eq:cc_schrodeq}
  \hat{H} \E^{\hat{T}} \ket{\Phi} = E \E^{\hat{T}} \ket{\Phi},
\end{align}
can be rewritten by left-multiplying by $\bra{\Phi}e^{-T}$ as,
\begin{align*}
  \bra{\Phi} \bar{H}_{\mathrm{CC}} \ket{\Phi} = E,
\end{align*}
where we define a coupled-cluster effective Hamiltonian,
\begin{align} \label{eq:cc_heff0}
  \bar{H}_{\mathrm{CC}} \equiv \E^{-\hat{T}} \hat{H} \E^{\hat{T}},
\end{align}
in which the wave operator, $\E^{\hat{T}}$, acts as a similarity transform on the Hamiltonian in the same way that $\hat{U}(s)$ acts to transform the Hamiltonian in SRG methods.  An important difference, however, is that the coupled cluster wave operator, which contains no de-excitations, is not unitary, and thus $\bar{H}$ is not Hermitian.

@@

In practice, the cluster operator $\hat{T}$ must be truncated for calculations to be computationally feasible.  In this work, we use only single and double excitations,
\begin{align*}
  \hat{T} = \hat{T}_1 + \hat{T}_2.
\end{align*}
This is known as coupled cluster singles and doubles (CCSD), with an asymptotic computational cost that scales like IM-SRG(2).  This truncation has been successfully applied to many problems in quantum chemistry \cite{RevModPhys.79.291} and nuclear physics \cite{0034-4885-77-9-096302}.  In addition, we also truncate the three-body effective Hamiltonian terms that are induced by the similarity transformation.  Figure \ref{fig:diagrams-ccsd} shows the diagrammatic representation of Eq.\ \eqref{eq:cc_heff1} in CCSD.

\begin{figure}
  \includegraphics{fig-diagrams-ccsd.pdf}
  \caption{(Color online) Diagrammatic representation of $\bar{H}$ of Eq.\ \eqref{eq:cc_heff1}, excluding terms involving the one-body interaction $\hat{H}_1$ and first-order terms involving only the bare Hamiltonian. Open circles represent the excitation cluster operators $\hat{T}_1$ and $\hat{T}_2$, and filled circles represent the two-body interaction $\hat{H}_2$.  As before, the diagrams are implicitly antisymmetrized (Hugenholtz diagrams).  Lines connected to $\hat{T}$ are always directed upward because they represent an excitation operator while the directions of external lines connected to $\hat{H}_2$ are unconstrained. }
  \label{fig:diagrams-ccsd}
\end{figure}
